\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I wish to express my deepest gratitude to my supervisor, Damir Filipović, for his guidance and continuous support during these five years. This thesis greatly benefited from his many valuable comments and flow of smart ideas. He guided me and I learned a lot from him about doing research. For this, I am truly grateful.

Special thanks go to professor Michael Rockinger who convinced me to pursue a doctorate degree. He took me under his wing since my Bachelor studies and helped me becoming the researcher I am today. This thesis would not exist without him.

I would like to acknowledge the rest of my thesis committee, the professors Pierre Collin-Dufresne, Andreas Fuster and Simon Scheidegger for their advice and comments.

I am also thankful to the professors Elena Perazzi and Damien Challet. I was their TA for several years and they helped me become a better teacher.

During these years I had the chance to work with extremely nice and intelligent people. I am thankful to my colleagues and friends Antoine Didisheim and Coralie Jaunin for the countless chess games and `bridge tours` around the campus.

I would like to thank my family: my parents Jacques and Sonia, my sister Isabelle and her husband Edward and my fiancée Cathy for their unconditional love and for bearing all my endless monologues about my latest algorithms. I dedicate this thesis to them.

\bigskip
 
\noindent\textit{Lausanne, \today}
\hfill M.-A.~D.
